\documentclass[12pt]{article}

\usepackage{sbc-template}
\usepackage{graphicx,url}
\usepackage[utf8]{inputenc}
\usepackage[brazil]{babel}
\usepackage[latin1]{inputenc}


\sloppy

\title{Vision-aided implementation of an Alexa List}

\author{
  Joseph A. P. Quino\inst{1},
  Fabio A. T. Madueno\inst{1},
  Jonathan\inst{1},
}


\address{
  Escola Politécnica da Universidade de São Paulo\\
  \email{\{joseph.pena, fabio.torres, jonathan.dos.santos.da.silva\}@usp.br}
}

\begin{document}

\maketitle

\input{chapters/01-abstract}
\input{chapters/02-introduction}
\input{chapters/03-methodology}
\input{chapters/04-results}
\input{chapters/05-conclusion}

\section{References}
\bibliographystyle{sbc}
% \bibliography{references/refs}

\begin{thebibliography}{}

\bibitem{smith2020} 
Smith, J. (2020). Proximity Retailing and Consumer Convenience: The Rise of Localized Markets. \textit{Journal of Retail Management}, 34(2), 123-145.

\bibitem{jones2019}
Jones, A., Brown, K., \& Taylor, L. (2019). Voice Assistants in Smart Homes: A Study of User Interactions with Alexa. \textit{International Journal of Human-Computer Interaction}, 45(4), 567-580.

\bibitem{doe2021}
Doe, R., et al. (2021). The Role of Virtual Assistants in Smart Homes: An Overview of Current Applications. \textit{Journal of Smart Technology}, 7(3), 45-67.

\bibitem{lee2020}
Lee, S., \& Brown, M. (2020). Integrating Computer Vision with Voice Assistants: Opportunities in Retail. \textit{Proceedings of the IEEE International Conference on Smart Systems}, 233-240.

\bibitem{wang2022}
Wang, X., et al. (2022). AI-Powered Vision Systems for Retail: A Review of Image Recognition Technologies. \textit{ACM Transactions on Intelligent Systems}, 12(1), 89-102.

\bibitem{chen2023}
Chen, Y., \& Patel, R. (2023). Cloud Computing and Visual Recognition in Retail Environments. \textit{Journal of Cloud Technologies}, 10(5), 78-92.

\end{thebibliography}

\end{document}
